---
title: "Detective Example"
format:
  revealjs:
    theme: custom.scss
    highlight-style: atom-one
    slideNumber: true
revealjs-plugins:
  - detective
---

```{r}
#| echo: false
#| eval: true
library(ggplot2)
```

# Welcome to Detective

## Highlight the code

Do you know how to create a plot?

:::: {.columns}
::: {.column width="40%"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::

::: {.column width="60%"}
```{r}
#| echo: false
#| eval: true
#| fig-height: 9
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point() +
  theme_grey(base_size = 20)
```
:::
::::

## Highlight the code

First, use `ggplot` function to select the data

::::: {.columns}
:::: {.column width="40%"}
:::{.detective data-detective-search="ggplot"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::
::::

:::: {.column width="60%"}
```{r}
#| echo: false
#| eval: true
#| fig-height: 9
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point() +
  theme_grey(base_size = 20)
```
::::
:::::


## Highlight the code

Then, use `aes` function to select the variables

::::: {.columns}
:::: {.column width="40%"}
:::{.detective data-detective-search="ggplot, aes"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::
::::

:::: {.column width="60%"}
```{r}
#| echo: false
#| eval: true
#| fig-height: 9
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point() +
  theme_grey(base_size = 20)
```
::::
:::::

## Highlight the code

Finally, use `geom_*` function to create a geometric element

::::: {.columns}
:::: {.column width="40%"}
:::{.detective data-detective-search="ggplot, aes, geom_point"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::
::::

:::: {.column width="60%"}
```{r}
#| echo: false
#| eval: true
#| fig-height: 9
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point() +
  theme_grey(base_size = 20)
```
::::
:::::

# Oh, that's nice!

## Highlight the code

Use `.detective` and `data-detective-search` to search words to highlight

::::: {.columns}
:::: {.column width="40%"}
:::{.detective data-detective-search="ggplot, aes, geom_point"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::
::::

:::: {.column width="60%"}
```
:::{.detective data-detective-search="ggplot, aes, geom_point"}

your chunk here...

:::
```
::::
:::::

## Highlight the code

Use `data-detective-bg-color` to modify the background color

::::: {.columns}
:::: {.column width="40%"}
:::{.detective data-detective-search="ggplot, aes, geom_point" data-detective-bg-color="#4287f5"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::
::::

:::: {.column width="60%"}
```
:::{.detective data-detective-search="ggplot, aes, geom_point" data-detective-bg-color="#4287f5"}

your chunk here...

:::
```
::::
:::::

:::::: {.fragment}
Use hex colors or CSS variables

::::: {.columns}
:::: {.column width="40%"}
:::{.detective data-detective-search="ggplot, aes, geom_point" data-detective-bg-color="var(--r-primary-color)"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::
::::

:::: {.column width="60%"}
```
:::{.detective data-detective-search="ggplot, aes, geom_point" data-detective-bg-color="var(--r-primary-color)"}

your chunk here...

:::
```

_* see custom.scss_
::::
:::::
::::::

## Highlight the code

Combine multiple `.detective`

::::: {.columns}
:::: {.column width="40%"}
:::{.detective data-detective-search="ggplot"}
:::{.detective data-detective-search="aes" data-detective-bg-color="var(--r-primary-color)"}
:::{.detective data-detective-search="geom_point" data-detective-bg-color="black" data-detective-code-color="#fff"}
```{r}
#| echo: true
#| eval: false
ggplot(data = iris) +
  aes(
    x = Sepal.Length,
    y = Sepal.Width
  ) +
  geom_point()
```
:::
:::
:::
::::

:::: {.column width="60%"}
```
:::{.detective data-detective-search="ggplot"}
:::{.detective data-detective-search="aes" data-detective-bg-color="var(--r-primary-color)"}
:::{.detective data-detective-search="geom_point" data-detective-bg-color="black" data-detective-code-color="#fff"}

your chunk here...

:::
:::
:::
```
::::
:::::

## Highlight the code

- `data-detective-search` search for words to highlight. Use `,` for multiple words.

- `data-detective-bg-color` background color. Default is `yellow`

- `data-detective-code-color` code color. Default is `black`
